Is It Possible to Steal Money Through USB-C?

### 2020-12-24 WOOT/Files/background.tex
revision of Motivation

\noindent\outline{USB2.0}\\
In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480 Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were supported in this revision. Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}. Though various peripherals were supported in USB 2.0, there was no reliable way to ensure a device is actually what it claims to be. This security flaw allowed attacks like Rubber Ducky\cite{rubber}.

@@

\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered.  As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}. But the divergent implementation give chance for attack like Rubber Ducky\cite{rubber} and our \tool.

>>>>

\noindent\outline{USB2.0}\\
In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480 Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were supported in this revision. Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}. Though various peripherals were supported in USB 2.0, there was no reliable way to identify the type of a device. This security flaw allowed attacks like Rubber Ducky\cite{rubber}.

@@

\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered.  As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}. But the divergent implementations give chance for attack like Rubber Ducky\cite{rubber} and our \tool.

### 2020-12-24 WOOT/Files/badusb.tex
revision of Motivation

\section{\tool}
\label{sec:badusb}
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take use of the \textit{default trust} given by computers to HIDs, pretend normal USB devices as HIDs and uitilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lacking of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

In this work, we utilized the new features of USB-C to address the problems above.
Benefiting from USB-C, we simulated vedio card and thus obtained the video stream of UI to perform accurate attacks.

>>>>

\section{\tool}
\label{sec:badusb}
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks\hongyi{disk is not HID}, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

In this work, we utilized the new features of USB 3.x \cite{usb31} \cite{usb32} to address the problems above.
Benefiting from latest protocol, we simulated video card and thus obtained the video stream to perform accurate attacks.
